Scientific Reports Title to see here (20 words or less)

### 2016-09-20 draft1.tex
added Morris plots

\subsection{Global Sensitivity}
We used the Morris method of sampling to generate a family of parameter sets, ranging from $\pm$25\% of the nominal parameter values, with the exception of $h_0$, which was bounded between [.8, 2.0], corresponding to a resting heart rate between 48 and 120 bpm.\cite{morris1991factorial} We found that this range of parameters resulted in physiologically acceptable heart rates. As heart rates are a function of time, it was neccessary for us to collapse the time dimension to perform sensitivity analysis. We used fPCA (functional principal component analysis) to convert the heart rate curves into weights ($\omega_i$) and eigenfunctions $(\xi_i(t))$ so that $h_j(t)=\sum_i \omega_i \xi_i(t)$, and then performed sensitivity analysis on the weights. \cite{sumner2012methodology}

@@

The model used has several shortcomings. This model oversimplifies the process of heart rate regulation. It does not include cardiac sypathetic afferrent reflex, which is sensitive to both mechanical and chemical inputs. \cite{du2007love} It can only be used for short time scales, as it does not include the slower acting renin-agiotensin-aldostrone system, which determines blood volume, and therefore blood pressure. \cite{boron2016medical} The model only considers two vassoctive agents when there are many more and does not attempt to capture the effects of respiration rate.  Nevertheless, it does captures the dynamics of the system at short time scales.
\section*{Methods}
All calculations were carried out Ubunutu 16.04 using Julia version .0.4.5, with 7.7 GB of available RAM on a Intel Core i7-6700 CPU @ 3.40GHz. Differential equations were solved using the ODE package, with solvers ode23 and ode78, with an absolute and relative tolerance of $10^{-8}$. Single objective optimization was perfomed using the Nelder Mead algorithm, as implimented in the Julia package NLopt, and multiobjective optimization was performed using the POETs package.

@@

>>>>

\subsection{Global Sensitivity}
We used the Morris method of sampling to generate a family of parameter sets, ranging from $\pm$25\% of the nominal parameter values, with the exception of $h_0$, which was bounded between [.8, 2.0], corresponding to a resting heart rate between 48 and 120 bpm.\cite{morris1991factorial} We found that this range of parameters resulted in physiologically acceptable heart rates. As heart rates are a function of time, it was neccessary for us to collapse the time dimension to perform sensitivity analysis. We used fPCA (functional principal component analysis) to convert the heart rate curves into weights ($\omega_i$) and eigenfunctions $(\xi_i(t))$ so that $h_j(t)=\sum_i \omega_i \xi_i(t)$, and then performed sensitivity analysis on the weights generated for each patient. \cite{sumner2012methodology} We then grouped the patients by cluster, and calculated the average of $\mu^*$, the estimate of the mean of distrubution of the absolute values of the elementry effects. For each cluster, we calculated the overall standard deviation, $\sigma$, by summing all of the variances and then taking the square root. \cite{1_normal sum distribution} The results are shown in \ref{fig:Cluster1Morris} and \ref{fig:Cluster2Morris}.

@@

The model used has several shortcomings. This model oversimplifies the process of heart rate regulation. It does not include cardiac sypathetic afferrent reflex, which is sensitive to both mechanical and chemical inputs. \cite{du2007love} It can only be used for short time scales, as it does not include the slower acting renin-agiotensin-aldostrone system, which determines blood volume, and therefore blood pressure. \cite{boron2016medical} The model only considers two vassoctive agents when there are many more and does not attempt to capture the effects of respiration rate.  Nevertheless, it does captures the dynamics of the system at short time scales.
\section*{Methods}
All calculations were carried out Ubunutu 16.04 using Julia version .0.4.5, with 7.7 GB of available RAM on a Intel Core i7-6700 CPU @ 3.40GHz. Differential equations were solved using the ODE package, with solvers ode23 and ode78, with an absolute and relative tolerance of $10^{-8}$. Single objective optimization was perfomed using the Nelder Mead algorithm, as implimented in the Julia package NLopt, and multiobjective optimization was performed using the POETs package. FPCA calculations were carried out through the use of the Rcall package using the R package FDApace.

@@

\begin{figure}[ht]
                \centering
        \includegraphics[width=\linewidth]{figures/MorrisPlotN100Cluster1}
       \caption{Cluster 1 Morris Plot, with N =100}
       \label{fig:Cluster1Morris}
\end{figure}

\begin{figure}[ht]
                \centering
        \includegraphics[width=\linewidth]{figures/MorrisPlotN100Cluster2}
       \caption{Cluster 2 Morris Plot, with N =100}
       \label{fig:Cluster2Morris}
\end{figure}
